---
title: "gameproject-cpp-cmake-conan-entt-bgfx-imgui"
author: "hedskul"
date: "`r Sys.Date()`"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.path = "figs/"
)
```
## REQUIREMENTS

conan
cmake
bgfx
imgui

## Installation guide

``` bash
# hello world
conan install . --output-folder=out/build/x64-Debug --build=missing -s build_type=Debug -s compiler.cppstd=17
conan profile list
conan profile show default
conan profile update settings.compiler.cppstd=17 default
```

## README is created using rmarkdown, knitr, and renv

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

1: Install R <https://cran.rstudio.com/>

2: Install RStudio RStudio requires R 3.6.0+. Choose a version of R that matches your computer’s operating system. <https://posit.co/download/rstudio-desktop/>

3 Recreate RStudio environment. RStudio: File -\> Open Project Browse to README.Rproj

**File - Open Project**

4 R Console:

``` r
install.packages("renv")
renv::restore()
```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# `{r a} # R #`

# `{python b} # Python #`

# `{dot c} # GraphViz #`

# `{mermaid d} # Mermaid #`

# `{bash e} # Bash #`

# `{julia f} # Julia #`

# `{Rcpp g} # Rcpp #`

# `{sql connection=} # SQL #`

# `{stan output.var=} # Stan #`
